---
title: "COVID-19 in the United States"
output: html_document
author: Scyler, Camden, Judy, Alexis
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, dev = 'pdf')
```


```{r include = FALSE}

timeseries <- read.csv('data/time_series_covid19_confirmed_US.csv', stringsAsFactors = 
                     FALSE)

source('./scripts/chart-1.R')
source('./scripts/chart-2.R')
```



## Introduction

COVID-19 has altered the world immeasurably. Schools and many workforces have been shift to become digitized and travel has been restricted. Mask use has been mandated by the government in many areas in the United States. With no end in sight of coronavirus cases dissipating, our group stems to give a visual presentation of COVID-19 incidence rates, as well as explore the correlation between tobacco use and COVID-19 incidence on difference ethnicity as a way to promote sources that promote equity.

## Summary

Summary Text goes here

<br />


## Table

Render your table and describe pertinent observations found in it

<br />


### Coronavirus in the United States (Chart 1)

This chart shows total COVID-19 cases across the United States, in the beginning of August, 2020. The map shows hotspots across the country where COVID-19 is more rampant.

```{r echo = F, fig.width = 9}
render_leaf_plot(timeseries)
```

<br />

### Coronavirus and United States Market Performance

This grid of charts demonstrates how the U.S markets had been impacted by the coronavirus. As you can see during the initial outbreak of coronavirus, the markets plunged more than 30% in a matter of weeks. Then you can see the market rapidly recovery and hitting all time highs in the S&P.

```{r echo = F, fig.width=9, fig.height=6}
dow_data <- read.csv('data/dow-jones-data.csv', stringsAsFactors = FALSE)
spy_data <- read.csv('data/S&P 500.csv', stringsAsFactors = FALSE)
owid_covid_data <- read.csv('data/owid-covid-data.csv', stringsAsFactors = FALSE)


covid_data <- owid_covid_data %>%
  group_by(location) %>%
  filter(location == 'United States') %>%
  mutate(formatDate = as.Date(date))


m_data <- dow_data %>% 
  mutate(formatDate = as.Date(Date, format='%m/%d/%Y'))

s_data <- spy_data %>% 
  mutate(formatDate = as.Date(Date, )) %>%
  mutate(spyClose = Close) %>%
  select(formatDate, spyClose)


df <- covid_data %>% inner_join(m_data, by = 'formatDate') %>%
  inner_join(s_data, by = 'formatDate')



render_chart2(df)



```

<br />


### Chart3

Chart 3 description

```{r echo = F}

```


